A Reduced Order Model for Porous Media Flows: Coupling Linear Regression with Principal Component Analysis (PCA) using High-Order Singular Value Decomposition (HOSVD) in Upscaling Calculations for Permeability in Reservoir Simulations

### 2018-12-03 Papers/AppliedMaths2018/Resubmission/Stochastic_Upscaling_UK_AMM_2018b.tex
files to be modified in the next 250min

Figure~\ref{fig:Saturationfield@t=1.15s} compares phase 1 saturation distribution for all the cases at $t=1.15s$. Generally, saturation distribution for all cases closely resemble each other with arithmetic and harmonic mean (Figs.~\ref{fig:Saturationfield@t=1.15s}(b) and (c)) being the most identical. Albeit, closer inspection will reveal that there is more displacement in Fig.~\ref{fig:Saturationfield@t=1.15s}(b) compared to (c). This is logical giving that the block mean values calculated for arithmetic mean is higher than that for harmonic mean. However, the important feature of Figs.~\ref{fig:Saturationfield@t=1.15s}(b) and (c) is that they poorly represent the BaseCase (Fig.~\ref{fig:Saturationfield@t=1.15s}(a)) at the top left hand corner of block $K2$.

>>>>

Figure~\ref{fig:Saturationfield@t=1.15s} compares phase 1 saturation distribution for all cases at $t=1.15s$. Generally, saturation distribution for all cases closely resemble each other with arithmetic and harmonic mean (Figs.~\ref{fig:Saturationfield@t=1.15s}b-c) being nearly identical. Albeit, closer inspection will reveal that there is more displacement in Fig.~\ref{fig:Saturationfield@t=1.15s}b compared to Fig.~\ref{fig:Saturationfield@t=1.15s}c. This is logical giving that the block mean values calculated for arithmetic mean is higher than that for harmonic mean. However, the important feature of Figs.~\ref{fig:Saturationfield@t=1.15s}b-c is that they poorly represent the BaseCase (Fig.~\ref{fig:Saturationfield@t=1.15s}a) at the top left hand-side corner of block $K2$.
